Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-04-01 ConferencePaper/DraftEdwardsWoods.Rnw

Variable and Data Description:

@@

  \begin{itemize}
    \item Differences in thermostat settings
    \item difference in cooking behavior x
    \item difference in reported AC use

>>>>

Variable and Data Description: 
Residential Energy Consumption Survey national data 2009 (RECS) was utilitized for this portion of the project. 12083 observations are included in the data, of which 11395 are included in the structure-tenure model. Weights provided in the data set were utilized to account from sample stratification.
  Combining dwelling type (dwltype) and the binary response variable ownrent, Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, and mobile home. Mobile homes are notable for having considerably fewer observations than other categories and were ultimately dropped from the model. 
  The model is based on the following variables: income, resident ages, education, rental assistence, and ethnicity and a variable for HUD complaints by state.  Householder race was interacted with income and  HUD complaints.  Logged, midpoints, are used for income. Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college, Associate’s, Bachelor’s, Master;s, Professional, and Doctorate degree.  The ethnicity variable is from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, other, and more than one race.  
  Over twice as many households choose to own their homes compared to renters.  As well we see that the majority of households, more than all other categories combined, live in single family detached houses (See Appendix).  Behind single family houses, large apartment complexes were the most likely dwelling types chosen.  Notably, apartments in general, were more commonly rented than owned as compared to the opposite for each other dwelling type.
	With respect to respondent education attainment, percentages of each category (see appendix) do differ from what can be expected.  It is entirely likely that this is an example of the survey effect on selection of respondents, i.e. that individuals with higher education attainment are more likely to respond to mailed surveys.

@@

  \begin{itemize}
    \item Differnces in thermostat settings x

    \item difference in cooking behavior x
    \item difference in reported AC use
